Leveraging Grover's Algorithm for Efficient Prime Decomposition

### 2025-03-02 LaTeX/paper.tex
Updated paper outline

@@

@@

The text on the final page should be arranged so that both columns are
approximately the same length.

>>>>

\section{Goals}

Demonstration of quantum advantage, or at least determination of
the problem scale at which quantum advantage will pull ahead.

\section{Literature Review}

Discuss existing methods of SP factoring- both quantum and classical.

Mention reference paper, QFT arithmetic, CUDA-Q docs, shor's, grover's.

@@

What have we learned so far, what does it mean, at what problem scale might
we see quantum advantage based on our results, etc.

@@

Implementation of the optimization with M, S, p, and q, rather than just 
a and b from N.
